An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/trans.tex

\para{Formal Intermediate Representation.}

An additional problem is that configuration files sometimes contain a simple version of the {\tt {if-then}} which 
sets under which conditions some actions should be applied.

The formal grammar we use for our intermediate representation presented in the following. 
Firstly, we make a list of the possible types for a configuration file. This is present in 
Secondly, we

@@

\com{Note that typing is also a system module than 
can be easily extended to support more types. 
In that case the user will need to provide rules for type inference 
and probability distributions for values where type inference is ambiguous.
}

>>>>

In general, the templates work as follows: if there are two entries ${\tt {k1 = v1}}$ and 
${\tt {k2 = v2}}$, let $t(X, Y)$ be a template that can be applied to those values (wrt. their types).
If $t(v1, v2)$ holds, \ie the template states is valid for those concrete values, then we will add a rule
$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a correlation between variables.

With the help of probabilistic types we addressed ambiguities during the parsing phase. A next problem that we need to solve
is that configuration files sometimes contain a simple version of the {\tt {if-then}}, that 
sets under which conditions some actions should be applied. Therefore, we also add this guard during the parsing phase. The meaning 
of the guard is that, before deriving a rule, we first check if the guard is true.

To summarize, the translator translates every entry ${\tt {k = v}}$ in a configuration file into a quadruple 
$$(g,k,v,\textsf{List}[p_1:\tau_1, \ldots, p_n:\tau_n])$$

\iffalse
The formal grammar we use for our intermediate representation presented in the following. 
Firstly, we make a list of the possible types for a configuration file. This is present in 
Secondly, we

@@

\com{Note that typing is also a system module than 
can be easily extended to support more types. 
In that case the user will need to provide rules for type inference 
and probability distributions for values where type inference is ambiguous.
}
\fi
